{\TheTitle}

### 2017-07-11 greedy_hamiltonian_second_revision/chapters/1.introduction.tex
second revision added

Convectional reduced basis techniques, such as proper orthogonal decomposition (POD) \cite{Kunisch:2002er,Atwell:2001ja,Ravindran:2002hn}, require the exploration of the entire parameter space. This leads to a very expensive and often impractical offline {\edit stage} when dealing with multi-dimensional parameter domains. On the other hand, sampling techniques, usually of a greedy nature, search through the parameter space selectively, guided by an error estimate to certify the accuracy of the basis. This approach, accompanied with an efficient sampling procedure, {\edit balances the cost} of computation with the overall accuracy of the reduced-basis \cite{Cuong:2005gd,Rozza:2005ie,Anonymous:2016wl}.

>>>>

Convectional reduced basis techniques, such as {\blue the} Proper Orthogonal Decomposition (POD) \cite{Kunisch:2002er,Atwell:2001ja,Ravindran:2002hn}, require the exploration of the entire parameter space. This leads to a very expensive and often impractical offline {\edit stage} when dealing with multi-dimensional parameter domains. On the other hand, sampling techniques, usually of a greedy nature, search through the parameter space selectively, guided by an error estimate to certify the accuracy of the basis. This approach, accompanied with an efficient sampling procedure, {\edit balances the cost} of computation with the overall accuracy of the reduced-basis \cite{Cuong:2005gd,Rozza:2005ie,Anonymous:2016wl}.

### 2017-07-11 greedy_hamiltonian_second_revision/chapters/2.mor.tex
second revision added

\subsection{Proper Orthogonal Decomposition} \label{chap:MoOr.PrOr:1}
Let $\mathbf x (t_i,\omega_j)$ with $i=1,\dots,m$ and $j=1,\dots,n$ be a finite number of samples, referred to as \emph{snapshots}, from the solution manifold (\ref{eq:MoOr:2}). If we {\edit assume} that a reduced basis $V$ is provided, the projection operator from $\mathbb R^n$ onto the reduced space can be constructed as $VV^T$. The proper orthogonal decomposition (POD) requires the total error of projecting all the snapshots onto the reduced space to be {\edit minimized}. The POD basis of size $k$ is thus the solution to the optimization problem
\begin{equation} \label{eq:MoOr:6}
\begin{aligned}
& \underset{V\in \mathbb R^{n\times k}}{\text{minimize}}
& & \| S - VV^TS\|_F \\
& \text{subject to}
& & V^TV = I_k
\end{aligned}
\end{equation}
Here $S$ is the snapshot matrix, containing snapshots $\mathbf x(t_i,\omega_j)$ in its columns, $\|\cdot \|_F$ is the Frobenius norm and $I_k$ is the identity matrix of size $k$. According to {\edit Schmidt-Mirsky-Eckart-Young theorem \cite{Markovsky:2011:LRA:2103589}}, the solution to (\ref{eq:MoOr:6}) is equivalent to the truncated singular value decomposition (SVD) of the snapshot matrix $S$ given by
\begin{equation} \label{eq:MoOr:7}
	V = \sigma_1 u_1 v^T_1 + \cdots + \sigma_k u_k v^T_k.
\end{equation}
Here $\sigma_i, u_i$ and $v_i$ are the singular values, the left singular vectors, and the right singular vectors of $S$, respectively {\edit \cite{Markovsky:2011:LRA:2103589} }.

\subsection{Discrete Empirical Interpolation Method (DEIM)} \label{chap:MoOr.DEIM:1} \nocite{Chaturantabut:2010cz}
In this section we {\edit discuss the efficiency} of evaluating nonlinearities {\edit in the context of} projection based reduced models. Suppose that the right hand side in (\ref{eq:MoOr:1}) is of the form $\mathbf f(t,\mathbf x , \omega) = L\mathbf x + \mathbf g(t,\mathbf x ,\omega)$, where $L\in \mathbb R^{n\times n}$ reflects the linear part, and $\mathbf g$ is a nonlinear function. Now {\edit assume that} a $k$-dimensional reduced basis $V$ is provided. The reduced system takes the form
\begin{equation} \label{eq:MoOr:8}
	\frac{d}{dt} \mathbf y = \underbrace{(WV)^{-1} L V}_{\tilde L} \mathbf{y} + \underbrace{(WV)^{-1} \mathbf g(t,V\mathbf y,\omega)}_{\tilde N (\mathbf y)}.
\end{equation}
Here, $\tilde L$ is a $k\times k$ matrix which can be computed before time integration of the reduced system. However, {\edit the} evaluation of $\tilde N (\mathbf y)$ has a complexity that depends on $n$, the size of the original system. Suppose that the evaluation of $\mathbf g$ with $n$ components has the complexity $\alpha(n)$, for some function $\alpha$. Then the complexity of evaluating $\tilde N(\mathbf y)$ is $\mathcal{O}(\alpha(n) + 4nk)$ which consists of 2 matrix-vector operations and the {\edit evaluation of the nonlinear function, i.e. the evaluation of the nonlinear terms can be as expensive as solving the original system.}

>>>>

\subsection{Proper Orthogonal Decomposition} \label{chap:MoOr.PrOr:1}
Let $\mathbf x (t_i,\omega_j)$ with $i=1,\dots,m$ and $j=1,\dots,n$ be a finite number of samples, referred to as \emph{snapshots}, from the solution manifold (\ref{eq:MoOr:2}). If we {\edit assume} that a reduced basis $V$ is provided, the projection operator from $\mathbb R^n$ onto the reduced space can be constructed as $VV^T$. The proper orthogonal decomposition (POD) requires the total error of projecting all the snapshots onto the reduced space to be {\edit minimized}. The POD basis of size $k$ is thus the solution to the optimization problem
\begin{equation} \label{eq:MoOr:6}
\begin{aligned}
& \underset{V\in \mathbb R^{n\times k}}{\text{minimize}}
& & \| S - VV^TS\|_F \\
& \text{subject to}
& & V^TV = I_k
\end{aligned}
\end{equation}
Here $S$ is the snapshot matrix, containing snapshots $\mathbf x(t_i,\omega_j)$ in its columns, $\|\cdot \|_F$ is the Frobenius norm and $I_k$ is the identity matrix of size $k$. According to {\blue the} {\edit Schmidt-Mirsky-Eckart-Young theorem \cite{Markovsky:2011:LRA:2103589}}, the solution to (\ref{eq:MoOr:6}) is equivalent to the truncated singular value decomposition (SVD) of the snapshot matrix $S$ given by
\begin{equation} \label{eq:MoOr:7}
	V = \sigma_1 u_1 v^T_1 + \cdots + \sigma_k u_k v^T_k.
\end{equation}
Here $\sigma_i, u_i$ and $v_i$ are the singular values, the left singular vectors, and the right singular vectors of $S$, respectively {\edit \cite{Markovsky:2011:LRA:2103589} }.

\subsection{Discrete Empirical Interpolation Method (DEIM)} \label{chap:MoOr.DEIM:1} \nocite{Chaturantabut:2010cz}
In this section we {\edit discuss the efficiency} of evaluating nonlinearities {\edit in the context of} projection based reduced models. Suppose that the right hand side in (\ref{eq:MoOr:1}) is of the form $\mathbf f(t,\mathbf x , \omega) = L\mathbf x + \mathbf g(t,\mathbf x ,\omega)$, where $L\in \mathbb R^{n\times n}$ reflects the linear part, and $\mathbf g$ is a nonlinear function. Now {\edit assume that} a $k$-dimensional reduced basis $V$ is provided. The reduced system takes the form
\begin{equation} \label{eq:MoOr:8}
	\frac{d}{dt} \mathbf y = \underbrace{(W^TV)^{-1} L V}_{\tilde L} \mathbf{y} + \underbrace{(W^TV)^{-1} \mathbf g(t,V\mathbf y,\omega)}_{\tilde N (\mathbf y)}.
\end{equation}
Here, $\tilde L$ is a $k\times k$ matrix which can be computed before time integration of the reduced system. However, {\edit the} evaluation of $\tilde N (\mathbf y)$ has a complexity that depends on $n$, the size of the original system. Suppose that the evaluation of $\mathbf g$ with $n$ components has the complexity $\alpha(n)$, for some function $\alpha$. Then the complexity of evaluating $\tilde N(\mathbf y)$ is $\mathcal{O}(\alpha(n) + 4nk)$ which consists of 2 matrix-vector operations and the {\edit evaluation of the nonlinear function, i.e. the evaluation of the nonlinear terms can be as expensive as solving the original system.}

### 2017-07-11 greedy_hamiltonian_second_revision/chapters/3.ham.tex
second revision added

{\edit Let $(\mathcal M,\Omega)$ be a symplectic manifold and suppose that $H:\mathcal M \to \mathbb R$ is a smooth scalar function. The differential of $H$, denoted by $\mathbf dH$, defines a 1-form on $\mathcal M$. The nondegeneracy of $\Omega$ implies that there is a unique vector field $X_H$, \emph{Hamiltonian vector field }\cite{da2003introduction,Marsden:1999ck}, on $\mathcal M$ such that}
\begin{equation} \label{eq:Hasy:1}
	\edit i_{X_H} \Omega = \mathbf dH, 
\end{equation}
{\edit where $i_{X_H} \Omega$ is the interior product of $X_H$ with $\Omega$, i.e., that requiring}
\begin{equation}
	\edit \Omega(X_H,Y) = \mathbf dH(Y),
\end{equation}
{\edit for any vector field $Y$ on $\mathcal M$.} Note that when $\edit \mathcal M$ belongs to a Euclidean space then $\mathbf d H = \nabla_z H$. The equations of evolution are then defined by
\begin{equation} \label{eq:Hasy:2}
	\dot z = X_H(z)
\end{equation}
and known as \emph{Hamilton's equation} \cite{Marsden:1999ck}. A fundamental feature of Hamiltonian systems is the conservation of the Hamiltonian along integral curves on $\edit \mathcal M$. To emphasize the importance of this property we recall {\edit \cite{Marsden:1999ck}}

@@

For the case where the symplectic manifold is also a linear vector space, the pair $({\edit \mathcal M},\Omega)$ is also referred to as a \emph{symplectic vector space}. We {\edit need} the following theorems regarding symplectic vector spaces and refer the reader to \cite{de2006symplectic,Marsden:1999ck,de2006symplectic,Silva01lectureson} for detailed proofs.

{\edit
\begin{theorem} \label{theorem:Hasy:1.1} \cite{Marsden:1999ck}
If $(V,\Omega)$ is a symplectic vector space then $\Omega$ is a constant form, that is $\Omega_z$ is independent of $z\in V$. 
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.2} \cite{Marsden:1999ck}
If $(V,\Omega)$ is a finite-dimensional symplectic manifold then $V$ is even dimensional.
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.3} \cite{de2006symplectic}
(The Symplectic Gram-Schmidt) If $(V,\Omega)$ is a $2n$-dimensional symplectic vector space, then there is a basis $e_1,\dots e_n,f_1, \dots , f_n$ of $V$ such that
\begin{equation} \label{eq:Hasy:4}
\begin{aligned}
	& \Omega(e_i,e_j) = 0 = \Omega(f_i,f_j), \quad & i\neq j,\\
	& \Omega(e_i,f_j) = \delta_{ij}, & i\leq i,j \leq n.
\end{aligned}
\end{equation}
where $\delta$ is the Kronecker's delta function. Moreover if $V = \mathbb{R}^{2n}$ we can choose basis vectors $\{e_i,f_i\}_{i=1}^n$ such that
\begin{equation} \label{eq:Hasy:5}
	\Omega(v_1,v_2) = v_1^T \mathbb J_{2n} v_2, \qquad v_1,v_2\in \mathbb R^n,
\end{equation}
with $\mathbb J_{2n}$ being the symplectic matrix, defined as
\begin{equation} \label{eq:Hasy:6}
	\mathbb{J}_{2n} = 
	\begin{pmatrix}
		0_n & I_n \\
		-I_n & 0_n
	\end{pmatrix}.
\end{equation}
Here $I_n$ and $0_n$ is the identity matrix and the zero square matrix of size $n$, respectively.
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.4} \cite{Marsden:1999ck}
The classical inner product $\langle \cdot,\cdot \rangle:\mathbb R^{2n}\times \mathbb R^{2n}\to \mathbb R$ can be written in terms of the 2-form as
\begin{equation}
	\langle v,u \rangle = \Omega(\mathbb J_{2n}v,u),\quad \forall u,v \in \mathbb R^{2n}.
\end{equation}
\end{theorem}
}

{\edit 
\begin{definition}  \cite{de2006symplectic}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space and $E\subset V$ is a subspace. Then the symplectic complement of $E$ inside $V$ is defined as
\[
	E^{\perp} := \{ v\in V |\ \Omega(v,e) = 0,\ \forall e\in E \}
\]
\end{definition}
Note that $E \cap E^{\perp}$ is not empty in general. 
\begin{definition} \cite{de2006symplectic}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space. A subspace $E\subset V$ is called a Lagrangian subspace inside $V$ if $E = E^\perp$.
\end{definition}
\begin{theorem} \label{theorem:Hasy:1.5} \cite{abraham1978foundations}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space. If $E\subset V$ is a Lagrangian subspace then $dim(E)=\frac 1 2dim(V)$. Here $dim$ denotes the dimension of the subspace.
\end{theorem}
\begin{definition}
A basis of $(V,\Omega)$ is called orthosymplectic if it is both a symplectic basis and an orthogonal basis with respect to the classical scalar product.
\end{definition}
\begin{theorem} \label{theorem:Hasy:1.6}  \cite{da2003introduction}
Suppose $(V,\Omega)$ is a $2n$ dimensional symplectic vector space and $E\subset V$ is a Lagrangian subspace. Then there is an orthosymplectic basis for $V$.
\end{theorem}
\begin{proof}
Starting from a Lagrangain subspace in $E \subset V$ an orthosymplectic basis can be easily constructed. By Theorem \ref{theorem:Hasy:1.5} $E$ is $n$ dimensional. Suppose that $\{ e'_1,\dots, e'_n \}$ is a basis for $E$, using the classical Gram-Schmidt orthogonalization process we can construct an orthonormal basis $\{ e_1,\dots,e_n \}$. Define a new set of vectors $f_1 = \mathbb J_{2n}^Te_1$, $f_2 =\mathbb J_{2n}^T e_2$, $\dots$, $f_n= \mathbb J_{2n}^Te_n$. We have
\begin{equation}
	\langle f_i, f_j \rangle = e_i^T \mathbb J_{2n} {\mathbb J_{2n}}^T e_i = \delta_{ij}, \quad \langle f_i, e_j \rangle = e_i^T \mathbb J_{2n} e_j = 0, \quad i,j=1,\dots,n,
\end{equation}
where we used the fact that $\mathbb J_{2n} {\mathbb J_{2n}}^T = I_{2n}$ in the first identity and the second identity is due to the fact that the basis $\{ e_1,\dots,e_n \}$ forms a Lagrangian subspace. This shows that the set $\{ e_1,\dots,e_n \}\cup \{ f_1,\dots,f_n \}$ forms an orthonormal basis. Also, it can be easily verified that this is a symplectic basis. Thus $\{ e_1,\dots,e_n \}\cup \{ f_1,\dots,f_n \}$ is an orthosymplectic basis.
\end{proof}
\begin{theorem} \label{theorem:Hasy:1.7} \cite{Marsden:1999ck}
On a finite-dimensional symplectic vector space the relationship (\ref{eq:Hasy:1}) becomes 
\begin{equation} \label{eq:Hasy:7}
\left\{
\begin{aligned}
	&\dot {\mathbf z} = \mathbb{J}_{2n} \nabla_{\mathbf z} H(\mathbf z), \\
	& \mathbf z(0) = \mathbf z_0.
\end{aligned}
\right.
\end{equation}
or, by introducing the canonical coordinates $\mathbf z = (\mathbf q^T, \mathbf p^T)^T$,
\begin{equation} \label{eq:Hasy:8}
\left\{
\begin{aligned}
	&\dot {\mathbf q} = \nabla_{\mathbf p} H(\mathbf q,\mathbf p),\\
	&\dot {\mathbf p} = - \nabla_{\mathbf q} H(\mathbf q,\mathbf p).
\end{aligned}
\right.
\end{equation}
\end{theorem}
}

>>>>

{\edit Let $(\mathcal M,\Omega)$ be a symplectic manifold and suppose that $H:\mathcal M \to \mathbb R$ is a smooth scalar function. The differential of $H$, denoted by $\mathbf dH$, defines a 1-form on $\mathcal M$. {\blue The nondegeneracy of $\Omega$ implies that there is a unique vector field $X_H$, \emph{the Hamiltonian vector field }\cite{da2003introduction,Marsden:1999ck}, on $\mathcal M$ such that}
\begin{equation} \label{eq:Hasy:1}
	\edit i_{X_H} \Omega = \mathbf dH. 
\end{equation}
}
{\blue Here $i_{X_H} \Omega$ is the interior product of $X_H$ with $\Omega$, i.e.,}
\begin{equation}
	\edit \Omega(X_H,Y) = \mathbf dH(Y),
\end{equation}
{\edit for any vector field $Y$ on $\mathcal M$.} Note that when $\edit \mathcal M$ belongs to a Euclidean space then $\mathbf d H = \nabla_z H$. The equations of evolution are then defined by
\begin{equation} \label{eq:Hasy:2}
	\dot z = X_H(z)
\end{equation}
and known as \emph{Hamilton's equation} \cite{Marsden:1999ck}. A fundamental feature of Hamiltonian systems is the conservation of the Hamiltonian along integral curves on $\edit \mathcal M$. To emphasize the importance of this property we recall {\edit \cite{Marsden:1999ck}}

@@

For the case where the symplectic manifold is also a linear vector space, the pair $({\edit \mathcal M},\Omega)$ is also referred to as a \emph{symplectic vector space}. We {\edit need} the following theorems regarding symplectic vector spaces and refer the reader to \cite{de2006symplectic,Marsden:1999ck,Silva01lectureson} for detailed proofs.

{\edit
\begin{theorem} \label{theorem:Hasy:1.1} \cite{Marsden:1999ck}
If $(V,\Omega)$ is a symplectic vector space then $\Omega$ is a constant form, that is $\Omega_z$ is independent of $z\in V$. 
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.2} \cite{Marsden:1999ck}
If $(V,\Omega)$ is a finite-dimensional symplectic manifold then $V$ is even dimensional.
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.3} \cite{de2006symplectic}
(The Symplectic Gram-Schmidt) If $(V,\Omega)$ is a $2n$-dimensional symplectic vector space, then there is a basis $e_1,\dots e_n,f_1, \dots , f_n$ of $V$ such that
\begin{equation} \label{eq:Hasy:4}
\begin{aligned}
	& \Omega(e_i,e_j) = 0 = \Omega(f_i,f_j), \quad & i\neq j,\\
	& \Omega(e_i,f_j) = \delta_{ij}, & i\leq i,j \leq n.
\end{aligned}
\end{equation}
where $\delta$ is the Kronecker's delta function. {\blue Moreover, if $V = \mathbb{R}^{2n}$ then} we can choose basis vectors $\{e_i,f_i\}_{i=1}^n$ such that
\begin{equation} \label{eq:Hasy:5}
	\Omega(v_1,v_2) = v_1^T \mathbb J_{2n} v_2, \qquad v_1,v_2\in \mathbb R^n,
\end{equation}
with $\mathbb J_{2n}$ being the {\blue standard} symplectic matrix, defined as
\begin{equation} \label{eq:Hasy:6}
	\mathbb{J}_{2n} = 
	\begin{pmatrix}
		0_n & I_n \\
		-I_n & 0_n
	\end{pmatrix}.
\end{equation}
Here $I_n$ and $0_n$ is the identity matrix and the zero square matrix of size $n$, respectively.
\end{theorem}
\begin{theorem} \label{theorem:Hasy:1.4} \cite{Marsden:1999ck}
The classical inner product $\langle \cdot,\cdot \rangle:\mathbb R^{2n}\times \mathbb R^{2n}\to \mathbb R$ can be written in terms of the 2-form as
\begin{equation}
	\langle v,u \rangle = \Omega(\mathbb J_{2n}v,u),\quad \forall u,v \in \mathbb R^{2n}.
\end{equation}
\end{theorem}
}

{\edit 
\begin{definition}  \cite{de2006symplectic}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space and $E\subset V$ is a subspace. Then the symplectic complement of $E$ inside $V$ is defined as
\[
	E^{\perp} := \{ v\in V |\ \Omega(v,e) = 0,\ \forall e\in E \}
\]
\end{definition}
Note that $E \cap E^{\perp}$ is not empty in general. 
\begin{definition} \cite{de2006symplectic}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space. A subspace $E\subset V$ is called a Lagrangian subspace inside $V$ if $E = E^\perp$.
\end{definition}
\begin{theorem} \label{theorem:Hasy:1.5} \cite{abraham1978foundations}
Suppose $(V,\Omega)$ is a finite dimensional symplectic vector space. If $E\subset V$ is a Lagrangian subspace then $dim(E)=\frac 1 2dim(V)$. Here $dim$ denotes the dimension of the subspace.
\end{theorem}
\begin{definition}
A basis of $(V,\Omega)$ is called orthosymplectic if it is both a symplectic basis and an orthogonal basis with respect to the classical scalar product.
\end{definition}
\begin{theorem} \label{theorem:Hasy:1.6}  \cite{mehl2009perturbation,da2003introduction}
Suppose $(V,\Omega)$ is a $2n$ dimensional symplectic vector space and $E\subset V$ is a Lagrangian subspace. Then there is an orthosymplectic basis for $V$.
\end{theorem}
\begin{proof}
{\blue A detailed proof can be found in \cite{mehl2009perturbation}. Since the proof contains an insight to the construction of symplectic bases, we are going to restate the proof.} Starting from a Lagrangain subspace in $E \subset V$ an orthosymplectic basis can be easily constructed. By Theorem \ref{theorem:Hasy:1.5} $E$ is $n$ dimensional. Suppose that $\{ e'_1,\dots, e'_n \}$ is a basis for $E$, using the classical Gram-Schmidt orthogonalization process we can construct an orthonormal basis $\{ e_1,\dots,e_n \}$. Define a new set of vectors $f_1 = \mathbb J_{2n}^Te_1$, $f_2 =\mathbb J_{2n}^T e_2$, $\dots$, $f_n= \mathbb J_{2n}^Te_n$. We have
\begin{equation}
	\langle f_i, f_j \rangle = e_i^T \mathbb J_{2n} {\mathbb J_{2n}}^T e_j = \delta_{ij}, \quad \langle f_i, e_j \rangle = e_i^T \mathbb J_{2n} e_j = 0, \quad i,j=1,\dots,n,
\end{equation}
where we used the fact that $\mathbb J_{2n} {\mathbb J_{2n}}^T = I_{2n}$ in the first identity and the second identity is due to the fact that the basis $\{ e_1,\dots,e_n \}$ forms a Lagrangian subspace. This shows that the set $\{ e_1,\dots,e_n \}\cup \{ f_1,\dots,f_n \}$ forms an orthonormal basis. Also, it can be easily verified that this is a symplectic basis. Thus $\{ e_1,\dots,e_n \}\cup \{ f_1,\dots,f_n \}$ is an orthosymplectic basis.
\end{proof}
\begin{theorem} \label{theorem:Hasy:1.7} \cite{Marsden:1999ck}
On a finite-dimensional symplectic vector space the relationship (\ref{eq:Hasy:1}) becomes 
\begin{equation} \label{eq:Hasy:7}
\left\{
\begin{aligned}
	&\dot {\mathbf z} = \mathbb{J}_{2n} \nabla_{\mathbf z} H(\mathbf z), \\
	& \mathbf z(0) = \mathbf z_0.
\end{aligned}
\right.
\end{equation}
or, by introducing the canonical coordinates $\mathbf z = (\mathbf q^T, \mathbf p^T)^T$,
\begin{equation} \label{eq:Hasy:8}
\left\{
\begin{aligned}
	&\dot {\mathbf q} = \nabla_{\mathbf p} H(\mathbf q,\mathbf p),\\
	&\dot {\mathbf p} = - \nabla_{\mathbf q} H(\mathbf q,\mathbf p).
\end{aligned}
\right.
\end{equation}
\end{theorem}
}
